Data Preparation

### 2019-06-05 Data Preparation - Course Data.Rmd
make use of useful_functions file

library(tidyverse)
library(tidytext)
library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
library(magrittr)
```

@@

collapse_or       <- function(string) string %>% str_c(collapse = "|")
collapse_space    <- function(string) string %>% str_c(collapse = " ")

>>>>

library(tidyverse)
library(tidytext)
library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
library(magrittr)

load("Output/useful functions.RDATA")
```

@@

### 2019-06-05 Data Preparation - Student Data.Rmd
make use of useful_functions file

@@

```{r d_transcript, cache = TRUE}
d_transcript <- paste0("Input/Raw Grades/grades", 1 : 2, ".csv") %>%

@@

```{r d_transcript helper}
course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% paste(collapse = "|")

>>>>

load("Output/useful functions.RDATA")

@@

```{r d_transcript, cache = TRUE}
d_transcript <- str_c("Input/Raw Grades/grades", 1 : 2, ".csv") %>%

@@

```{r d_transcript helper}
course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% collapse_or
